\documentclass[11pt]{article}
\usepackage{enumerate}

\begin{document}

\centerline{\textbf{\LARGE Sprint 1-2 Retrospective 19.03.2018 - 13.04.2018}}

\section*{What did we learn?}
\begin{enumerate}
	\item Technical and technological aspect
		\begin{enumerate} 
			\item Docker, Libcluon, Javascript, HTML, CSS, catch-framework for unit testing, emscripten and websockets.
		\end{enumerate} 
	\item Process issues
		\begin{enumerate} 
			\item Need for a shared vision with PO.
			\item Need to adapt quickly to current circumstances, and changes.
		\end{enumerate}		
	\item Documentation related matters
		\begin{enumerate} 
			\item Started leaning LaTeX
		\end{enumerate}	
\end{enumerate} 

\section*{What worked well during this sprint?}
\begin{enumerate}
	\item Meeting times not too long 
	\item No (kinda) hardware issues 
	\item Good cooperation between the team members
\end{enumerate} 

\section*{What went wrong/poorly this sprint?}
\begin{enumerate}
	\item Due to extensive obstacles in respective user stories, it was hard to follow the process due to our estimations did not match up with provided deadlines from the course managers.
	\item Pretty much did not follow the process
	\item The scrum master (Justinas) should have put more focus on following the process and established guidelines
	\item Learning cmake and building docker images took awhile
\end{enumerate} 

\section*{What can be improved during the next sprint?}
\begin{enumerate}
	\item Standups on Slack
	\item Following the process
	\item Documentation of provided images was poor which resulted in a lot of unnecessary work generating virtually no value.
\end{enumerate} 


\section*{Was this sprint affected by unavailability of any members?}
Not really, yet, the easter break kind of generated an uncertainty of responsibilities and deliveries.

\end{document}
