\documentclass[11pt]{article}
\usepackage{enumerate}

\begin{document}

\textbf{\LARGE Sprint 4 Retrospective 2018.04.20 - 2018.04.27}

\section*{What did we learn?}
\begin{enumerate}
	\item Technical and technological aspect
		\begin{enumerate} 
			\item It’s difficult to integrate hardware/software
		\end{enumerate} 
	\item Process issues
		\begin{enumerate} 
			\item Deviation in shared vision between development teams, in regards to requirements. 
			\item A lot of communication and testing is required to ensure platooning with the other team/car, the amount could have been reduced by doing so incrementally since the start of the project
			\item Had a number of dependencies that interconnect with each other. For example to test platooning, the V2V protocol had to work, for the protocol to work the WiFi had work (etc)
		\end{enumerate}		
	\item Documentation related matters
		\begin{enumerate} 
			\item Most of the sprint was spent on testing platooning, so no new documentation lessons were learnt 
		\end{enumerate}	
\end{enumerate} 

\section*{What worked well during this sprint?}
\begin{enumerate}
	\item The communication between team members was good, and the level of dedication and willingness to work together.
\end{enumerate} 

\section*{What went wrong/poorly this sprint?}
\begin{enumerate}
	\item Having effective meetings with the other team trying to get the following to work, caused by hardware issues
	\item Knowledge sharing
\end{enumerate} 

\section*{What can be improved during the next sprint?}
\begin{enumerate}
	\item Sprint planning
	\item Code quality
	\item Daily standups were lost during this sprint. Try to keep them even though there’s crunchtime goin’ on
	\item We could have smaller user stories and more knowledge sharing within the group so that anyone could join any stories when their own is done
\end{enumerate} 


\section*{Was this sprint affected by unavailability of any members?}
No, the team met every day

\end{document}
